Flabby and injective objects in toposes

### 2022-02-16 paper-flabby-objects.tex
typo

\begin{rem}\label{rem:constant-flabby}
Although we will see in \XXX{number} and in Section~\ref{sect:in-eff} that there is some
relation between flabby sets and~$\neg\neg$-separated sets, neither notion
encompasses the other. The set~$\Omega$ is flabby, but might fail to
be~$\neg\neg$-separated; the set~$\ZZ$ is~$\neg\neg$-separated, even discrete,
but might fail to be flabby. This can abstractly be seen by adapting the proof of
Proposition~\ref{prop:taboo}. An explicit model in which~$\ZZ$ is not flabby
can be obtained by picking any topological space~$T$ such that~$H^1(T,
\underline{\ZZ}) \neq 0$, where~$\underline{\ZZ}$ is the constant sheaf with
stalks~$\ZZ$. For instance, the space~$T$ could be connected (such that every
global section is constant) while having an open which is the disjoint union of
two connected components. Then the sheaf~$\underline{\ZZ}$ is not
flabby and hence, by Proposition~\ref{prop:flabby-sheaves-objects} below, not a
flabby set from the internal point of view of~$\Sh(T)$.
\end{rem}

@@

\subsection{On the existence of enough flabby modules}

@@

It is worth noting that, because the internal language machinery was at that
point not as well-developed as it is today, Harting had to go to considerable
length to construct internal direct sums of abelian group
objects~\cite{harting:coproduct}, and in order to verify that taking internal
direct sums is faithful she felt the need to employ Barr's
metatheorem~\cite[Theorem~1.7]{harting:effacements}. Nowadays we can verify
both statements by simply carrying out an intuitionistic proof in the case of
the topos of sets and then trusting the internal language to obtain the
generalization to arbitrary elementary toposes with a natural numbers object.

>>>>

\begin{rem}\label{rem:constant-flabby}
A set~$X$ is \emph{$\neg\neg$-separated} if and only
if~$\neg\neg(x=y)\Rightarrow x=y$ for all elements~$x,y \in X$.
Although Section~\ref{sect:enough-flabby-modules} presents some
relation between flabby sets and~$\neg\neg$-separated sets, neither notion
encompasses the other. The set~$\Omega$ is flabby, but might fail to
be~$\neg\neg$-separated; the set~$\ZZ$ is~$\neg\neg$-separated, even discrete,
but might fail to be flabby. This can abstractly be seen by adapting the proof of
Proposition~\ref{prop:taboo}. An explicit model in which~$\ZZ$ is not flabby
can be obtained by picking any topological space~$T$ such that~$H^1(T,
\underline{\ZZ}) \neq 0$, where~$\underline{\ZZ}$ is the constant sheaf with
stalks~$\ZZ$. For instance, the space~$T$ could be connected (such that every
global section is constant) while having an open which is the disjoint union of
two connected components. Then the sheaf~$\underline{\ZZ}$ is not
flabby and hence, by Proposition~\ref{prop:flabby-sheaves-objects} below, not a
flabby set from the internal point of view of~$\Sh(T)$.
\end{rem}

@@

\subsection{On the existence of enough flabby modules}
\label{sect:enough-flabby-modules}

@@

It is worth noting that, because the internal language machinery was at that
point not as well-developed as it is today, Harting had to go to considerable
length to construct internal direct sums of abelian group
objects~\cite{harting:coproduct}, and in order to verify that taking internal
direct sums is faithful she appealed to Barr's
metatheorem~\cite[Theorem~1.7]{harting:effacements}. Nowadays we can verify
both statements by simply carrying out an intuitionistic proof in the case of
the topos of sets and then trusting the internal language to obtain the
generalization to arbitrary elementary toposes with a natural numbers object.
